A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$

### 2025-04-06 paper_v02/article.tex
latex time tables

The $52.7\%$ increase in performance from the basic to the optimized \proglang{Zig} implementation is a good result, showcasing the effectiveness of the optimizations. Another test was conducted, wth the same data and settings as the previous one, but getting the elapsed time inside every time scale. These results are presented in Fig.~\ref{fig:elapsed_tws}.

@@

Figure \ref{fig:elapsed_tws} shows the elapsed computation time difference from the Basic to the optimized version of the algorithm increases as the time scale increases. If the test was conducted with a bigger time series, and with larger time scales the difference would be even more significant.

>>>>

The $52.7\%$ increase in performance from the basic to the optimized \proglang{Zig} implementation is a good result, showcasing the effectiveness of the optimizations. Another test was conducted, wth the same data and settings as the previous one, but getting the elapsed time inside every time scale. These results are presented in Fig.~\ref{fig:elapsed_tws_04}.

@@

Figure \ref{fig:elapsed_tws_04
} shows the elapsed computation time difference from the Basic to the optimized version of the algorithm increases as the time scale increases. If the test was conducted with a bigger time series, and with larger time scales the difference would be even more significant.
